Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-11-29 paper/paper.tex
some progress

\begin{definition}[R\'enyi Differential Privacy (RDP)]\label{def:rdp}
A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1,\db_2$ that differ in exactly one row, we have
\[
D_\alpha(M(\db_1) \Vert M(\db_2)) \leq \gamma
\]
where $D_\alpha$ is the R\'enyi divergence\cite{van2014renyi} of order $\alpha$.

TODO: formula def

\end{definition}

\begin{theorem}[RDP of the Gaussian Mechanism\cite{feldman2018privacy,mironov2017renyi}]
The Gaussian Mechanism satisfies $(\alpha, \alpha \frac{\Delta^2_f}{2 \sigma^2})$-RDP.

TODO: sensitivity
\end{theorem}

@@

@@

The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.

TODO: add noise to marginal not database

>>>>

\begin{definition}[R\'enyi Differential Privacy (RDP)]\label{def:rdp}
A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1,\db_2$ that differ in exactly one row, we have
\[
D_\alpha(M(\db_1) \Vert M(\db_2)) \leq \gamma
\]
where $D_\alpha(P \Vert Q)$ is the R\'enyi divergence\cite{van2014renyi,van2010renyi,li2016renyi} of order $\alpha$ between discrete probability distributions $P$ and $Q$, defined on $\mathcal{X}$:
\[
D_\alpha(P \Vert Q) := \frac{1}{\alpha - 1} \text{log} \sum_{x \in \mathcal{X}} {P(x)}^\alpha {Q(x)}^{1-\alpha}
\]
\end{definition}

\begin{theorem}[RDP of the Gaussian Mechanism\cite{feldman2018privacy,mironov2017renyi}]
The Gaussian Mechanism satisfies $(\alpha, \alpha \frac{\Delta^2_f}{2 \sigma^2})$-RDP, where $\Delta_f$ denotes the sensitivity\cite{dwork2014algorithmic} of $f$.

TODO: define sensitivity?

\end{theorem}

@@

TODO: indicator thing

@@

The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to some marginals of $\db$ such that it satisfies some differential privacy guarantees and outputting another database $\db'$, such that the $L_1$ errors between some marginals $C_i$s of $\db$ and $\db'$ is small; that is, their marginals $M_{C_i}(\db),M_{C_i}(\db')$ are similar.
